---
title: "03-events"
author: "Amanda Pennino"
date: "2024-05-02"
output: html_document
---


#Input
# * Rain Gauge precipitation (15 min)

#Output
# * Delineated storm events


Notes:
"From 2012 to 2015, eight typhoons were sampled and the basic information
was collected, including the total precipitation amount (P), duration (D), average intensity of rainfall
(RIavg), maximum 3-h rainfall amount (Pmax3h), total runoff (Q), peak flow (Qmax), runoff ratio (Q/P),
and the antecedent 7-day rainfall (AP7day). In the literature, these are considered to be factors affecting
event water transit time and event water fraction [23–25]"
  Hrachowitz, M.; Soulsby, C.; Tetzlaff, D.; Malcolm, I.A.; Schoups, G. Gamma distribution models for transit
  time estimation in catchments: Physical interpretation of parameters and implications for time-variant transit
  time assessment. Water Resour. Res. 2010, 46, W10536. [CrossRef]
  24. Klaus, J.; McDonnell, J.J. Hydrograph separation using stable isotopes: Review and evaluation. J. Hydrol.
  2013, 505, 47–64. [CrossRef]
  25. Segura, C.; James, A.L.; Lazzati, D.; Roulet, N.T. Scaling relationships for event water contributions and
  transit times in small-forested catchments in Eastern Quebec. Water Resour. Res. 2012, 48, W07502. [CrossRef]

```{r}
library(tidyverse)
library(lubridate)

```



#DOWNLOAD THE LATEST PRECIP DATASET
- Data set title: Hubbard Brook Experimental Forest: 15-minute Precipitation Measurements, 2011 - present.
- Grab code and run in console: https://portal.edirepository.org/nis/codeGeneration?packageId=knb-lter-hbr.277.8&statisticalFileType=r
- Last downloaded from edi: 05/10/2024
- Data is in millimeters
- Gauge spelled as "gage"

#######CHANGE THE OUTPUT FILE TO output_precip

```{r}

datesRG <- read_csv("~/projects/DSS/HBEF/HBEF_repo/rg_dates.csv")

#Rain Gauge 19 (June-August 2011)
rg19 <- read_csv("timeseries/edi_precip/RG19.csv")

#Rain Gauge 1 (August 2011-2016)
rg1 <- read_csv("timeseries/edi_precip/RG1.csv")
first_1 <- head(rg1$DateTime, n = 1)
  
#Rain Gauge 4 (August 2016-2020)
rg4 <- read_csv("timeseries/edi_precip/RG4.csv")
first_4 <- head(rg4$DateTime, n = 1)


#Refine and combine
rg19 <- rg19 %>%
  filter(DateTime < first_1)

rg1 <- rg1 %>%
  filter(DateTime < first_4)

precip <- bind_rows(rg19, rg1, rg4)

#write.csv(precip, "timeseries/precipWS3_15min.csv")

#aggregate to 1-hour data


p <- precip %>% 
  select(DateTime, precip)


p <- p %>% 
  mutate(DateTime = floor_date(DateTime, unit = "hour")) %>% 
  group_by(DateTime) %>% 
  summarise(precip = sum(precip))

#write.csv(p, "timeseries/precipWS3_1hr.csv")


```



# ID EVENTS
- Functions named in hydrun_fxns.R
- Notes on settings parameters: Minimum Interevent Time, runoff producing threshold (e.g., inches)


Minimum Inter-event Time Determination (IETD)
```{r}

p <- read_csv("timeseries/precipWS3_1hr.csv")
p <- p %>% select(DateTime, precip)


results_CVA <- CVA(Time_series = p, 
               Time_Step = 1,
               MaxIETD = 24)

IETD_CVA<-results_CVA$EITD
results_CVA$Figure



results_AutoA <- AutoA(Time_series = p,
                       Time_Step = 1)

results_AutoA$Figure
#where it comes to 0
IETD_AutoA = 14


```


Runoff producing rainfall events
```{r}
CN = 83.7
Pt_mm = (25400/CN)-254 #equation from Chin
Pt_inches = Pt_mm/25.4


```






